\chapter{Introduction}
\label{chap:introduction}
\section {Motivation}
In recent years, Automatic Speech Recognition (ASR) systems have improved
increasingly, being used in everyday applications: Siri, Google ASR 
\parencite {mcgrawgrauenstein2012}. However, most of such systems work
asynchronously in respect to output, computing the result after the utterance is already finished.
In the area of Human-Machine Interaction, 
where intermediate system reactions of ASRs are 
desirable,  incremental output of the intermediate results becomes increasingly
important. Benefits of  incremental speech recognition include post-processing
time savings, faster system feedback and more natural dialogue between humans
and intelligent systems. 

Commercial Google recognition
engine, working in incremental mode, produces accurate
results in non-specific domains, but demonstrates higher latency
\parencite{mcgrawgrauenstein2012}.  Non-commercial open source systems, like Sphinx-4, on the other hand, demonstrate very short delays and can be timed to specific
applications, but are less reliable in accuracy.

Moreover, Google results lacks timing information that can a great
benefit, for example, in robotics environment. In such kind of applications it
is often important to know at what time a particular word was said to relate and
refer the objects correctly to other non-verbal information, like gestures.
The challenge is to combine the advantages of both systems and to enrich
the Google results with timing information and try to overcome the latency
problem of Google ASR.
\section {Problem Statement}
The aim of this master thesis is to investigate the possibility of
timeliness and timing improvement of Google ASR
incremental results by developing an incremental speech recognizer, using a
combination of Google ASR \parencite
{mcgrawgrauenstein2012} and a Sphinx-4 speech recogniser
\parencite {baumannetal2009:naacl}. 
\section {Objectives}

The following objectives states, how the aim of the master thesis is going to be
addressed:
 \begin  {itemize}
   \item to align incremental results,coming from Google ASR, using a
   combination of Google and Sphinx ASRs,
   \item to evaluate timing results of forced alignment, comparing Google
   alone, Sphinx alone and Google + Sphinx combination, using evaluation
   metrics,
   \item to investigate the possibility for Google timeliness improvement in
   multiple source recogniser,
   \item to evaluate results of timeliness improvement, comparing Google alone,
   Sphinx alone and a Google + Sphinx combination.
 \end {itemize}


\section {Structure}
This master thesis is structured as follows. Chapter \ref{chap:introduction}give
a brief introduction of the research topic. Chapter \ref{ch:relatedWork}
provides review of state of the art scientific papers, related to the topic of
incrementality, general speech recognition and multiple source recognizers.
Chapter \ref{chap:terms} explains the terminology to be used in the context of this master thesis.  
In the first place there is a definition try of such terms as timing and
timeliness an an explanation of what kind of metrics are relevant to
evaluate their quality. Chapter \ref{ch:sphinx} describes the architecture of
CMU (Carnegie Mellon University) Sphinx-4 recognizer as a typical ASR.
Implementation of the Google+Sphinx recognizer is discussed in the chapter
\ref{chap:implem} of this paper. Chapter \ref{chap:res} describes the evaluation approach and results,received for Google+Sphinx recognizer, as
well as for Google and Sphinx alone.
Chapter \ref{chap:concl} summarizes the most important ideas of the master
thesis and provides some points for discussion and future work.
